Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-22 cav2017/cav2017.tex
text

We consider models of physical plants expressed as ordinary differential equations (ODEs), 
with full state information (namely where we have access to all the model variables):  
%
\begin{align}
\label{eq:ode}
\dot{x}(t) = Ax(t)+ B u(t), \quad x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}, 
\end{align}
where $t \in \mathbb R_0^+$, 
where $A$ and $B$ are matrices that fully specify the continuous plant, 
and with initial states set as $x(0)$. 
Eq.~\eqref{eq:ode} is soundly discretised in time (as shown in the Appendix) into
%
\begin{align}
\label{eq:plant}
x_{k+1} = A_d x_k+ B_d u_k. 
\end{align} 
where $k \in \mathbb N$, 
and with initial state $x_{0}=x(0)$.

@@

A discrete-time system is asymptotically stable if and only if all the roots 
of the characteristic polynomial ({\it i.e.}, the eigenvalues) are inside of 
the unity circle, {\it i.e.}, their absolute value are less than 
one~\cite{astrom1997computer}. In this paper, we express 
the stability specification $\phi_{stability}$ in terms of  
Jury's criterion \cite{fadali}. A detailed description of this 
specification can be found in the Appendix~\ref{sec:appendix-stability}.

%-------------------------------
\subsection{Safety specifications for cyber-physical systems}
\label{ssec:safety}
%-------------------------------

We also require that the closed-loop system meets safety specifications. 
A safety specification establishes bounds for the states, such that 
the controller $K$ must maintain the states within a given lower and upper 
bound for any initial state. Note that a stable system is not necessarily a
safe system, the state values may leave the safe states during the stabilization.

>>>>

We consider models of physical plants expressed as ordinary differential equations (ODEs), 
with full state information (namely where we have access to all the model variables):  
%
\begin{align}
\label{eq:ode}
\dot{x}(t) = Ax(t)+ B u(t), \quad x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}, 
\end{align}
where $t \in \mathbb R_0^+$, 
where $A$ and $B$ are matrices that fully specify the continuous plant, 
and with initial states set as $x(0)$. 
Eq.~\eqref{eq:ode} is soundly discretised in time (as shown in the Appendix) into
%
\begin{align}
\label{eq:plant}
x_{k+1} = A_d x_k+ B_d u_k. 
\end{align} 
where $k \in \mathbb N$, 
and with initial state $x_{0}=x(0)$. 
Later, we will deal with the issue of variable quantisation, as introduced by the ADC and DAC blocks.

@@

A discrete-time system as \eqref{eq:closedloopss} is asymptotically stable if and only if all the roots 
of the characteristic polynomial ({\it i.e.}, the eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity circle in the complex plane, 
{\it i.e.} iff their absolute value are less than one~\cite{astrom1997computer}. 
In this paper, we express the stability specification $\phi_{stability}$ in terms of a check known as Jury's criterion \cite{fadali}. 
This condition boils down to an easy algebraic formula to select the entries of matrix $K$, 
so that the closed-loop dynamics are shaped as desired. 
A detailed description of this specification can be found in the Appendix~\ref{sec:appendix-stability}.

%-------------------------------
\subsection{Safety specifications for dynamical systems}
\label{ssec:safety}
%-------------------------------

As mentioned earlier, 
in this work we are not bound to the synthesis of digital stabilising controllers -- 
a well known task in the literature on digital control system -- 
but target safety requirements with an overall approach that is sound and automated. 
More specifically, 
we require that the closed-loop system \eqref{eq:closedloopss} meets given safety specifications. 
A safety specification establishes bounds for the states, such that 
the controller $K$ must maintain the states within a given lower and upper 
bound for any initial state. Note that a stable system is not necessarily a
safe system, the state values may leave the safe states during the stabilization.
